Creating the ``r params$package_name`` R package

### 2025-06-05 create-FSHybridPLS.Rmd
nipals commented
and improved a little bit

```{r eval=FALSE, include=FALSE}
nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
  # 1. initialize the storage
  rho <- xi <- delta <- nu  <- sigma <- eta <- list()
  E <- V_star <- eigen_val <-list()
  fitted_value_W <- fitted_value_y <-list()
  resid_y <- W_now <- list() #data for iteration
  first_eigen_val <- mse_W <- mse_y <-rep(NA, n_iter)

  # 2. constraint matrix is the same at every iteration
  constr_mat      <- get_constraint_matrix_hybrid(W, lambda) 
  constr_mat_chol <- t(chol(constr_mat))

  W_now[[1]] <- W
  y_now <- y
  final_succesful_iteration <- 0
  for (l in 1:n_iter) {
    #cat(paste("#############################################", "\n"))
    if(verbose==T)cat(paste(l, "th component", "\n"))

    # STEP 1. calculate pls score
    pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
    if(!is.list(pls_result_now)){break}

    xi[[l]] <- pls_result_now$xi # pls component. Section 3.2
    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]]) # pls scores : n_sample * 1 matrix

    # STEP 2. residulize
    # residualize predictor: hybrid (W) on scalar (rho) linear regression with n_sample observations
    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]]) #single obs of hybrid predictor

    fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
    W_now[[l+1]] <- subtr(W_now[[l]], fitted_value_W[[l]])
    # residualize resoponse
    nu[[l]] <- LSE_ptws(y_now, rho[[l]]) #scalar on scalar linear regression with n_sample observations
    fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
    y_now <- y_now - fitted_value_y[[l]]
    resid_y[[l]] <- y_now

    #check mean norm
    #mse_W[l] <- mean_sum_sqrd(W_now[[l]])
    #mse_y[l] <- norm(y_now,"2")

    #cat("W:", mse_W[l], "\n")
    #cat("y:",  mse_y[l], "\n\n")

    # STEP 3.
    sigma[[l]] <- xi[[l]]
    if (l == 1) {
      eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
    }else{ # if l > 1
      for (u in 1:(l - 1)){
        sigma[[l]] <- subtr( sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]) )
      } #end of u-loop
      eta[[l]] <- add(eta[[l-1]], sigma[[l]], nu[[l]])
    }#if statement

    # just for records.
    E[[l]] <- pls_result_now$E # for monitoring symetricity
    V_star[[l]] <- pls_result_now$V_star
    eigen_val[[l]] <- pls_result_now$eigen_val
    first_eigen_val[l] <- eigen_val[[l]][1]
    final_succesful_iteration <- l
  }# for loop: l
}
```
## Documenting the package and building

>>>>

```{r eval=FALSE, include=FALSE}
#' Iterative Penalized NIPALS Algorithm for Hybrid PLS
#'
#' Performs iterative extraction of PLS components using a penalized NIPALS algorithm
#' for hybrid predictor objects that include both scalar and functional data.
#'
#' At each iteration:
#' \enumerate{
#'   \item Computes the first penalized PLS component using \code{get_pls_comp}.
#'   \item Computes PLS scores via hybrid inner products.
#'   \item Residualizes both predictors and response with respect to the extracted scores.
#'   \item Orthogonalizes and accumulates loading vectors to construct final linear predictors.
#' }
#' The same constraint matrix (computed once) is used across all iterations.
#'
#' @param W A \code{predictor_hybrid} object containing scalar and functional predictors.
#' @param y A numeric response vector of length equal to \code{W$n_sample}.
#' @param n_iter An integer specifying the number of PLS components (iterations) to compute.
#' @param lambda A numeric vector of smoothing parameters (length = number of functional predictors).
#' @param verbose Logical; if \code{TRUE}, prints progress for each component.
#'
#' @return This function operates by side effects. Internally, it constructs and updates:
#' \itemize{
#'   \item \code{xi}, \code{rho}, \code{delta}, \code{nu}: component vectors and regression effects,
#'   \item \code{sigma}, \code{eta}: orthogonalized components and accumulated prediction functions,
#'   \item \code{W_now}, \code{resid_y}: residualized predictor and response at each iteration,
#'   \item \code{E}, \code{V_star}, \code{eigen_val}: matrices for monitoring stability and eigenvalue progress.
#' }
#' The final number of successful iterations is tracked via \code{final_succesful_iteration}.
#'
#' @export
nipals_pen_hybrid <- function(W, y, n_iter, lambda, verbose) {
  # 1. Initialize storage
  rho <- xi <- delta <- nu  <- sigma <- eta <- list()
  E <- V_star <- eigen_val <- list()
  fitted_value_W <- fitted_value_y <- list()
  resid_y <- W_now <- list()
  first_eigen_val <- mse_W <- mse_y <- rep(NA, n_iter)

  # 2. Compute and store the constraint matrix once
  constr_mat <- get_constraint_matrix_hybrid(W, lambda)
  constr_mat_chol <- t(chol(constr_mat))

  # 3. Initialize residuals
  W_now[[1]] <- W
  y_now <- y
  final_succesful_iteration <- 0

  for (l in 1:n_iter) {
    if (verbose) cat(paste(l, "th component", "\n"))

    # Step 1: Compute penalized PLS direction and score
    pls_result_now <- get_pls_comp(W_now[[l]], y_now, constr_mat_chol, verbose)
    if (!is.list(pls_result_now)) break

    xi[[l]] <- pls_result_now$xi
    rho[[l]] <- hybrid_inner_prod(W_now[[l]], xi[[l]])

    # Step 2: Residualize predictor and response
    delta[[l]] <- LSE_hybrid(W_now[[l]], rho[[l]])
    fitted_value_W[[l]] <- fitted_value(delta[[l]], rho[[l]])
    W_now[[l + 1]] <- subtr(W_now[[l]], fitted_value_W[[l]])

    nu[[l]] <- LSE_ptws(y_now, rho[[l]])
    fitted_value_y[[l]] <- nu[[l]] * rho[[l]]
    y_now <- y_now - fitted_value_y[[l]]
    resid_y[[l]] <- y_now

    # Step 3: Orthogonalize and update prediction
    sigma[[l]] <- xi[[l]]
    if (l == 1) {
      eta[[l]] <- scalar_mul(sigma[[l]], nu[[l]])
    } else {
      for (u in 1:(l - 1)) {
        sigma[[l]] <- subtr(sigma[[l]], sigma[[u]], hybrid_inner_prod(delta[[u]], xi[[l]]))
      }
      eta[[l]] <- add(eta[[l - 1]], sigma[[l]], nu[[l]])
    }

    # Record diagnostics
    E[[l]] <- pls_result_now$E
    V_star[[l]] <- pls_result_now$V_star
    eigen_val[[l]] <- pls_result_now$eigen_val
    first_eigen_val[l] <- eigen_val[[l]][1]
    final_succesful_iteration <- l
  }
}

```
## Documenting the package and building
